\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}
\chapter*{Acknowledgements\label{sec:acknowledgements}}


\noindent\textit{I thank Professor Vardanega for his patience and for the invaluable support provided in the creation of this thesis, despite my black periods.}\\

\noindent\textit{I thank mum for always supporting me over this long period. Thanks for your strength and hugs.}\\

\noindent\textit{I thank dad for always being here, for his kindness and for being open to a comparison with my ideas.}\\

\noindent\textit{I thank Alberto, that will always be here, pandemics or meteors. David Murphy is nothing compared to you.}\\

\noindent\textit{I thank the old friends rediscovered and the new ones, especially Celeste, Cristi, Gianluca, Giovanni, Mirko and Sarah, without whose support I would have already dropped out of university.}\\

\noindent\textit{I thank Claudia for her poems, because she taught me the value of freedom.}\\

\noindent\textit{I thank the people who I lost and the ones who abandoned me, for making me understand how important being present for someone can be.}\\

\noindent\textit{I thank all the people who have welcomed me and taught me something in these two years, in particular true resilience and true consistency with their own ideas. Thanks to Matteo Gracis, to all the members of the NoBufale.it team and to the Students against the Green Pass.}\\

\noindent\textit{I thank Professors Andrea Camperio Ciani and Maristella Agosti for the life lessons, I will carry them in my luggage.}\\\\\\

\textit{Padova, 16 december 2021}
\hfill Matteo Marchiori